Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-08-25 article/article.Rmd
Commit 2024-08-25 19:11

BR <- readRDS("~/MANUSCRIPTS/02_enhancement/data/Model_CS_trend.Rds")
BR <-  unique(BR[typer == "BR SZA 55", .(year, pw_avg_mm, b, a)])
```

@@

Following the application of the above discussed methodology to the entire dataset 
($`r round(ST_total$wattGLB.N / 10^6,1)`$ million of one-minute GHI measurements),
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 2)`\,\%$ were identified as CE events and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
The highest recorded GHI due to CE was
$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding
to OI of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
<!-- The absolute strongest CE event had an OI of 
<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
The strongest CE event of
$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
clear sky threshold was observed on 
`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
In the following sections we are discussing the long-term trends and variability of
the CE events as well as of the corresponding OI and excess irradiation.

>>>>

BR <- readRDS("~/MANUSCRIPTS/02_enhancement/data/Model_CS_trend.Rds")
BR <-  unique(BR[typer == "BR SZA 55", .(year, pw_avg_mm, b, a)])
MC <- readRDS("~/MANUSCRIPTS/02_enhancement/data/Max_cases.Rds")
```

@@

$`r round(MC[Typ == "Max Glob", wattGLB],1)`\,\text{W}/\text{m}^2$
$`r strftime(MC[Typ == "Max Glob", Date], "%d\\ %B %Y")`\,\text{W}/\text{m}^2$
$`r round(MC[Typ == "Max Glob", GLB_diff],1)`\,\text{W}/\text{m}^2$
$`r round(100*MC[Typ == "Max Glob", GLB_ench],1)`\,\%$

$`r round(MC[Typ == "Max Enha", wattGLB],1)`\,\text{W}/\text{m}^2$
$`r strftime(MC[Typ == "Max Enha", Date], "%d\\ %B %Y")`\,\text{W}/\text{m}^2$
$`r round(MC[Typ == "Max Enha", GLB_diff],1)`\,\text{W}/\text{m}^2$
$`r round(100*MC[Typ == "Max Enha", GLB_ench],1)`\,\%$

Following the application of the above discussed methodology to the entire dataset 
($`r round(ST_total$wattGLB.N / 10^6,1)`$ million of one-minute GHI measurements),
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 2)`\,\%$ were identified as CE events and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
The highest recorded GHI due to CE was
$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$ on
 `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding to OI of 
$`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
!!!!$`r round(100*ST_daily[which.max(GLB_diff.max), GLB_ench.max], 1)`\,\%$.!!!!!
<!-- The absolute strongest CE event had an OI of 
<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
The strongest CE event of
$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
clear sky threshold was observed on 
`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
!!!$`r round(ST_daily[which.max(GLB_ench.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$!!!!
In the following sections we are discussing the long-term trends and variability of
the CE events as well as of the corresponding OI and excess irradiation.
